---
title: "Download Positron"
description: "Download Positron for Windows, macOS, or Linux. Free data science IDE supporting Python and R with automatic updates included."
format:
  html:
    include-in-header:
      - '_download.html'

---

```{r}
#| echo: false
#| warning: false

library(purrr)
library(glue)
library(httr)
library(jsonlite)

# Read release version from _environment
release_version <- Sys.getenv("RELEASE_VERSION")

# Create URLs
cdn_url <- "https://cdn.posit.co/positron/releases/" # Keep this in sync with cdnUrl in _download.html

#######################################################################################
# NOTE: please also check welcome.qmd and _download.html when updating the various URLs,
# to ensure that we are constructing these URLs consistently in both places.
#######################################################################################

windows_system_x64 <- glue("Positron-{release_version}-Setup-x64.exe")
windows_user_x64 <- glue("Positron-{release_version}-UserSetup-x64.exe")
windows_system_arm64 <- glue("Positron-{release_version}-Setup-arm64.exe")
windows_user_arm64 <- glue("Positron-{release_version}-UserSetup-arm64.exe")
macos_arm64 <- glue("Positron-{release_version}-arm64.dmg")
macos_x64 <- glue("Positron-{release_version}-x64.dmg")
debian_x64 <- glue("Positron-{release_version}-x64.deb")
debian_arm <- glue("Positron-{release_version}-arm64.deb")
redhat_x64 <- glue("Positron-{release_version}-x64.rpm")
redhat_arm <- glue("Positron-{release_version}-arm64.rpm")

urls <- list(
  win_sys_x64 = glue("{cdn_url}win/x86_64/{windows_system_x64}"),
  win_user_x64 = glue("{cdn_url}win/x86_64/{windows_user_x64}"),
  win_sys_arm64 = glue("{cdn_url}win/arm64/{windows_system_arm64}"),
  win_user_arm64 = glue("{cdn_url}win/arm64/{windows_user_arm64}"),
  mac_arm64 = glue("{cdn_url}mac/arm64/{macos_arm64}"),
  mac_x64 = glue("{cdn_url}mac/x64/{macos_x64}"),
  deb_x64 = glue("{cdn_url}deb/x86_64/{debian_x64}"),
  deb_arm64 = glue("{cdn_url}deb/arm64/{debian_arm}"),
  rpm_x64 = glue("{cdn_url}rpm/x86_64/{redhat_x64}"),
  rpm_arm64 = glue("{cdn_url}rpm/arm64/{redhat_arm}")
)

# Get checksums
checksum_data <- rlang::try_fetch(
  fromJSON(glue("{cdn_url}checksums/positron-{release_version}-checksums.json")),
  error = function(cnd) list(),
  warning = function(cnd) list()
)
all_installers <- list(
  windows_system_x64,
  windows_user_x64,
  windows_system_arm64,
  windows_user_arm64,
  macos_arm64,
  macos_x64,
  debian_x64,
  debian_arm,
  redhat_x64,
  redhat_arm
)
checksums <- map_chr(all_installers, ~ pluck(checksum_data, .))

# Get file sizes
cloudfront_headers <- map(urls, HEAD) |> map(headers)
file_sizes <- map(cloudfront_headers, "content-length") |>
  map(fs::fs_bytes) |>
  map_chr(as.character)

# Build download link HTML (avoids markdown escaping of URLs)
dl <- list(
  mac_arm64 = glue('<a href="{urls$mac_arm64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[5]}</a>'),
  mac_x64 = glue('<a href="{urls$mac_x64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[6]}</a>'),
  win_user_x64 = glue('<a href="{urls$win_user_x64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[2]}</a>'),
  win_sys_x64 = glue('<a href="{urls$win_sys_x64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[1]}</a>'),
  win_user_arm64 = glue('<a href="{urls$win_user_arm64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[4]}</a>'),
  win_sys_arm64 = glue('<a href="{urls$win_sys_arm64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[3]}</a>'),
  deb_x64 = glue('<a href="{urls$deb_x64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[7]}</a>'),
  deb_arm64 = glue('<a href="{urls$deb_arm64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[8]}</a>'),
  rpm_x64 = glue('<a href="{urls$rpm_x64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[9]}</a>'),
  rpm_arm64 = glue('<a href="{urls$rpm_arm64}" class="download-link"><i class="fa-solid fa-download" aria-hidden="true"></i> {file_sizes[10]}</a>')
)
```

Find out what you need to know before you [install](install.qmd) Positron, then download the desktop installer for your platform.

::: {#download-hero .download-hero data-version="`{r} release_version`"}

### [Recommended for you]{#hero-title}

[Detecting your operating system...]{#hero-subtitle .hero-subtitle}

::: {#hero-buttons}
:::

<p class="hero-legal">By downloading and using Positron, you agree to Positron's <a href="licensing.html">license agreement</a> and <a href="https://posit.co/about/privacy-policy/">privacy policy</a>.</p>

:::

## All platforms

<p class="hero-legal">By downloading and using Positron, you agree to Positron's <a href="licensing.html">license agreement</a> and <a href="https://posit.co/about/privacy-policy/">privacy policy</a>.</p>

```{r}
#| echo: false
#| results: asis

cat('<div class="download-cards">

<div id="card-macos" class="download-card">
<h4><i class="fa-brands fa-apple" aria-hidden="true"></i> macOS <span class="option-meta">11.0+</span></h4>
<div class="download-option">
<div class="option-label">Apple Silicon<br><span class="option-meta">(M-series)</span></div>
', dl$mac_arm64, '
</div>
<div class="download-option">
<div class="option-label">Intel</div>
', dl$mac_x64, '
</div>
</div>

<div id="card-windows" class="download-card">
<h4><i class="fa-brands fa-windows" aria-hidden="true"></i> Windows</h4>
<div class="download-group">
<p><strong>x64</strong> <span class="option-meta">(Windows 10+)</span></p>
<div class="download-option">
<div class="option-label">User install</div>
', dl$win_user_x64, '
</div>
<div class="download-option">
<div class="option-label">System install</div>
', dl$win_sys_x64, '
</div>
</div>
<div class="download-group">
<p><strong>ARM64</strong> <span class="option-meta">(Windows 11)</span></p>
<div class="download-option">
<div class="option-label">User install</div>
', dl$win_user_arm64, '
</div>
<div class="download-option">
<div class="option-label">System install</div>
', dl$win_sys_arm64, '
</div>
</div>
</div>

<div id="card-linux" class="download-card">
<h4><i class="fa-brands fa-linux" aria-hidden="true"></i> Linux</h4>
<div class="download-group">
<p><strong>x64</strong></p>
<div class="download-option">
<div class="option-label">.deb <span class="option-meta">(Ubuntu, Debian)</span></div>
', dl$deb_x64, '
</div>
<div class="download-option">
<div class="option-label">.rpm <span class="option-meta">(Red Hat, Fedora)</span></div>
', dl$rpm_x64, '
</div>
</div>
<div class="download-group">
<p><strong>ARM64</strong></p>
<div class="download-option">
<div class="option-label">.deb <span class="option-meta">(Ubuntu, Debian)</span></div>
', dl$deb_arm64, '
</div>
<div class="download-option">
<div class="option-label">.rpm <span class="option-meta">(Red Hat, Fedora)</span></div>
', dl$rpm_arm64, '
</div>
</div>
</div>

</div>')
```

<details class="checksums-section">
<summary>SHA-256 checksums</summary>

```{r}
#| echo: false
#| warning: false

checksum_table <- data.frame(
  Platform = c(
    "Windows 10, 11 x64 (system level install)",
    "Windows 10, 11 x64 (user level install)",
    "Windows 11 arm64 (system level install)",
    "Windows 11 arm64 (user level install)",
    "MacOS 11.0+ (arm64/Apple Silicon)",
    "MacOS 11.0+ (x64/Intel)",
    "Debian-based Linux x64 (Ubuntu 20+)",
    "Debian-based Linux arm64 (Ubuntu 20+)",
    "Red Hat-based Linux x64 (RHEL9)",
    "Red Hat-based Linux arm64 (RHEL9)"
  ),
  Installer = c(
    glue('<a href="{urls$win_sys_x64}">{windows_system_x64}</a>'),
    glue('<a href="{urls$win_user_x64}">{windows_user_x64}</a>'),
    glue('<a href="{urls$win_sys_arm64}">{windows_system_arm64}</a>'),
    glue('<a href="{urls$win_user_arm64}">{windows_user_arm64}</a>'),
    glue('<a href="{urls$mac_arm64}">{macos_arm64}</a>'),
    glue('<a href="{urls$mac_x64}">{macos_x64}</a>'),
    glue('<a href="{urls$deb_x64}">{debian_x64}</a>'),
    glue('<a href="{urls$deb_arm64}">{debian_arm}</a>'),
    glue('<a href="{urls$rpm_x64}">{redhat_x64}</a>'),
    glue('<a href="{urls$rpm_arm64}">{redhat_arm}</a>')
  ),
  Size = unname(file_sizes),
  check.names = FALSE
)

# `checksums` and `file_sizes` follow the same order as the rows above.
checksums_display <- substr(checksums, 1, 7)

checksum_table$`SHA-256` <- glue(
  '<span class="checksum" onclick="copyChecksum(\'{checksums}\', this)" title="Click to copy full checksum">{checksums_display}</span>'
)

knitr::kable(checksum_table, format = "html", escape = FALSE, row.names = FALSE)
```

</details>

Once you install Positron, it will [automatically check for updates moving forward](updating.qmd).

::: {.callout-note}
## Stay in the loop
Want to be notified about upcoming releases, new features, and community events? [Sign up for Positron updates](https://posit.co/positron-updates-signup/).
:::

## Positron Pro on Posit Workbench

[Posit Workbench](https://posit.co/products/enterprise/workbench/) 2025.09.0 and later includes support for Positron Pro. To configure and use Positron Pro on Posit Workbench, please see the [Posit Workbench Administration Guide](https://docs.posit.co/ide/server-pro/admin/positron_sessions/) and the [Positron Pro user guide](https://docs.posit.co/ide/server-pro/user/positron/getting-started/).

## Release notes

The current release of Positron is {{< env RELEASE_VERSION >}}.

{{< include release-notes/release.md >}}

## Older releases

Older releases [are available on GitHub](https://github.com/posit-dev/positron/releases), and you can also find the [release notes for previous versions](release-notes.qmd#older-releases).
