---
title: "Download Positron"
description: "Download Positron for Windows, macOS, or Linux. Free data science IDE supporting Python and R with automatic updates included."
format:
  html:
    include-in-header:
      - '_download.html'

---

```{r}
#| echo: false
#| warning: false

library(purrr)
library(glue)
library(httr)
library(jsonlite)

# Read release version from _environment
release_version <- Sys.getenv("RELEASE_VERSION")

# Create URLs
cdn_url <- "https://cdn.posit.co/positron/releases/" # Keep this in sync with cdnUrl in _download.html

#######################################################################################
# NOTE: please also check welcome.qmd and _download.html when updating the various URLs,
# to ensure that we are constructing these URLs consistently in both places.
#######################################################################################

windows_system_x64 <- glue("Positron-{release_version}-Setup-x64.exe")
windows_user_x64 <- glue("Positron-{release_version}-UserSetup-x64.exe")
windows_system_arm64 <- glue("Positron-{release_version}-Setup-arm64.exe")
windows_user_arm64 <- glue("Positron-{release_version}-UserSetup-arm64.exe")
macos_arm64 <- glue("Positron-{release_version}-arm64.dmg")
macos_x64 <- glue("Positron-{release_version}-x64.dmg")
debian_x64 <- glue("Positron-{release_version}-x64.deb")
debian_arm <- glue("Positron-{release_version}-arm64.deb")
redhat_x64 <- glue("Positron-{release_version}-x64.rpm")
redhat_arm <- glue("Positron-{release_version}-arm64.rpm")

urls <- list(
  win_sys_x64 = glue("{cdn_url}win/x86_64/{windows_system_x64}"),
  win_user_x64 = glue("{cdn_url}win/x86_64/{windows_user_x64}"),
  win_sys_arm64 = glue("{cdn_url}win/arm64/{windows_system_arm64}"),
  win_user_arm64 = glue("{cdn_url}win/arm64/{windows_user_arm64}"),
  mac_arm64 = glue("{cdn_url}mac/arm64/{macos_arm64}"),
  mac_x64 = glue("{cdn_url}mac/x64/{macos_x64}"),
  deb_x64 = glue("{cdn_url}deb/x86_64/{debian_x64}"),
  deb_arm64 = glue("{cdn_url}deb/arm64/{debian_arm}"),
  rpm_x64 = glue("{cdn_url}rpm/x86_64/{redhat_x64}"),
  rpm_arm64 = glue("{cdn_url}rpm/arm64/{redhat_arm}")
)

# Get checksums
checksum_data <- rlang::try_fetch(
  fromJSON(glue("{cdn_url}checksums/positron-{release_version}-checksums.json")),
  error = function(cnd) list(),
  warning = function(cnd) list()
)
all_installers <- list(
  windows_system_x64,
  windows_user_x64,
  windows_system_arm64,
  windows_user_arm64,
  macos_arm64,
  macos_x64,
  debian_x64,
  debian_arm,
  redhat_x64,
  redhat_arm
)
checksums <- map_chr(all_installers, ~ pluck(checksum_data, .))
checksums_short <- substr(checksums, 1, 7)

# Get file sizes
cloudfront_headers <- map(urls, HEAD) |> map(headers)
file_sizes <- map(cloudfront_headers, "content-length") |>
  map(fs::fs_bytes) |>
  map_chr(as.character)
```

## Positron on desktop

Find out what you need to know before you [install](install.qmd) Positron, then download the desktop installer for your platform.

::: {#download-hero .download-hero data-version="`{r} release_version`"}

### [Recommended for you]{#hero-title}

[Detecting your operating system...]{#hero-subtitle .hero-subtitle}

::: {#hero-buttons}
:::

:::

## All platforms

::: {.download-cards}

:::: {#card-macos .download-card}

#### {{< fa brands apple >}} macOS

::: {.download-option}
::: {.option-label}
Apple Silicon<br><span class="option-meta">(M-series)</span>
:::
<a href="`{r} urls$mac_arm64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[5]`</a>
:::

::: {.download-option}
::: {.option-label}
Intel
:::
<a href="`{r} urls$mac_x64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[6]`</a>
:::

::::

:::: {#card-windows .download-card}

#### {{< fa brands windows >}} Windows

::: {.download-group}
**x64** (most PCs)

::: {.download-option}
::: {.option-label}
User install
:::
<a href="`{r} urls$win_user_x64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[2]`</a>
:::

::: {.download-option}
::: {.option-label}
System install
:::
<a href="`{r} urls$win_sys_x64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[1]`</a>
:::
:::

::: {.download-group}
**ARM64** (Surface Pro, Snapdragon)

::: {.download-option}
::: {.option-label}
User install
:::
<a href="`{r} urls$win_user_arm64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[4]`</a>
:::

::: {.download-option}
::: {.option-label}
System install
:::
<a href="`{r} urls$win_sys_arm64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[3]`</a>
:::
:::

::::

:::: {#card-linux .download-card}

#### {{< fa brands linux >}} Linux

::: {.download-group}
**x64**

::: {.download-option}
::: {.option-label}
<span title="Ubuntu, Debian">.deb</span>
:::
<a href="`{r} urls$deb_x64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[7]`</a>
:::

::: {.download-option}
::: {.option-label}
<span title="RHEL, Fedora">.rpm</span>
:::
<a href="`{r} urls$rpm_x64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[9]`</a>
:::
:::

::: {.download-group}
**ARM64**

::: {.download-option}
::: {.option-label}
<span title="Ubuntu, Debian">.deb</span>
:::
<a href="`{r} urls$deb_arm64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[8]`</a>
:::

::: {.download-option}
::: {.option-label}
<span title="RHEL, Fedora">.rpm</span>
:::
<a href="`{r} urls$rpm_arm64`" class="download-link download-trigger">{{< fa download >}} `{r} file_sizes[10]`</a>
:::
:::

::::

:::

<details class="checksums-section">
<summary>SHA-256 checksums</summary>

```{r}
#| echo: false
#| warning: false

checksum_table <- data.frame(
  Platform = c(
    "macOS (Apple Silicon)", "macOS (Intel)",
    "Windows x64 (user install)", "Windows ARM64 (user install)",
    "Windows x64 (system install)", "Windows ARM64 (system install)",
    "Linux .deb x64", "Linux .deb ARM64",
    "Linux .rpm x64", "Linux .rpm ARM64"
  ),
  Installer = c(
    macos_arm64, macos_x64,
    windows_user_x64, windows_user_arm64,
    windows_system_x64, windows_system_arm64,
    debian_x64, debian_arm,
    redhat_x64, redhat_arm
  ),
  Size = c(
    file_sizes[5], file_sizes[6],
    file_sizes[2], file_sizes[4],
    file_sizes[1], file_sizes[3],
    file_sizes[7], file_sizes[8],
    file_sizes[9], file_sizes[10]
  ),
  check.names = FALSE
)

full_checksums <- c(
  checksums[5], checksums[6],
  checksums[2], checksums[4],
  checksums[1], checksums[3],
  checksums[7], checksums[8],
  checksums[9], checksums[10]
)

checksums_display <- substr(full_checksums, 1, 7)

checksum_table$`SHA-256` <- glue(
  '<span class="checksum-cell"><code>{full_checksums}</code><button title="Copy to Clipboard" class="code-copy-button"><i class="bi"></i></button></span>'
)

knitr::kable(checksum_table, format = "html", escape = FALSE, row.names = FALSE)
```

</details>

<br>

Once you install Positron, it will [automatically check for updates moving forward](updating.qmd).

::: {.callout-note}
## Stay in the loop
Want to be notified about upcoming releases, new features, and community events? [Sign up for Positron updates](https://posit.co/positron-updates-signup/).
:::

## Positron Pro on Posit Workbench

[Posit Workbench](https://posit.co/products/enterprise/workbench/) 2025.09.0 and later includes support for Positron Pro. To configure and use Positron Pro on Posit Workbench, please see the [Posit Workbench Administration Guide](https://docs.posit.co/ide/server-pro/admin/positron_sessions/) and the [Positron Pro user guide](https://docs.posit.co/ide/server-pro/user/positron/getting-started/).

## Release notes

The current release of Positron is {{< env RELEASE_VERSION >}}.

{{< include release-notes/release.md >}}

## Older releases

Older releases [are available on GitHub](https://github.com/posit-dev/positron/releases), and you can also find the [release notes for previous versions](release-notes.qmd#older-releases).
